On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-04 Manuscript/manuscript.tex
Manuscript Update (some comments I still have to address)

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$):
\jy{Any equation must be a part of a sentence and should be punctuated.}
\jy{Recall a blank line means a new paragraph.}
\jy{Define your response command with color and respond}

\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{l - 1}\} & \text{if } j = n - l + 2 ,\dots, n
    \end{cases}
\end{equation}
\jy{The ending index does not seem right}
The second implementation of moving block bootstrap was used in
this study, and moving block bootstrap in general had been found to yield the 
lowest error \jy{state we use it because it is implemented in package boot and
  cite boot}
\citep{radovanov2014comparison}.  
\jy{This reference is from a low-tier journal. Find something from a stronger journal?}
The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

@@

\paragraph{Bias Corrected and Accelerated (BCA) Bootstrap CI}
In this study, the BCA CI is an interval centered at the point estimator.
\eds{a different abbrevation/notation was used for this in the introduction}
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
$z_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$, let
$\hat{\theta}_{n, -i}$ be the statistic of the sample without the $i^{th}$
block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
 $\hat\theta_{BCA}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
A $(1 - \alpha)$ centered percentile \eds{BCA?} CI is
\[
(\hat\theta_{BCA}[\alpha/2], \quad
\hat\theta_{BCA}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
\jy{why is it called BCA?}

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, CI}$ and $\hat\theta_{U, CI}$ be the lower and upper bound,
respectively,  for $CI \in \{1, \ldots, n_{CI}\}$, where $n_{CI}$ is the number 
of CIs.
Then $cov = \#\{\hat\theta_{L, CI} < \theta < \hat\theta_{U, CI} \}/n_{CI}$,  
for $CI \in \{1, \ldots, n_{CI}\}$.
\eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
value of $CI$; consider using a summation of indicators with a different index}
The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

Block bootstrap is a useful method for estimating parameters of a time
series, from simple parameters like the mean to more complicated temporal
 dependence factors.
%The motivation for the study is the idea that block bootstrap procedure will
%perfectly estimate a parameter of a time series given an infinitely large
%sample. The goal for this study was to find what is a good enough finite
%sample length for block bootstrap estimation to recover the parameter of a
%time series at an acceptable rate.
We know theoretically that the block bootstrap procedure will
perfectly estimate \eds{? interval will correctly cover?  What does the theory 
actually say?} a parameter of a time series given an infinitely large
sample, so the goal for this study was to find the smallest finite
sample length $n$ of a time series in order for the block bootstrap procedure to 
recover its associated parameters at an acceptable rate.

Again, this \eds{what?} relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the two types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
percentile and $BC_a$ intervals exhibited coverage deterioration as $n$
increased.

>>>>

\newcommand{\jy}[1]{\textcolor{blue}{JY: #1}}
\newcommand{\eds}[1]{\textcolor{red}{EDS: (#1)}}
\newcommand{\mc}[1]{\textcolor{green}{MC: (#1)}}

@@

Alternatively, block-bootstrap can be done with overlapping or moving blocks.
Define moving blocks $Z_j = \{X_j, \ldots, X_{j + l - 1}\}$,
$j = 1, \ldots, n - l + 1$. Now we draw $k$ blocks from the $(n - l + 1)$
blocks
of $Z_j$'s with replacement and then align them in the order they were
picked
to form a block bootstrap sample. If $n$ is not a multiple of~$l$, the last
block selected will be reduced in size so that the final size of the
block bootstrap sample is $n$. It is also possible to implement moving block
bootstrap while allowing blocks to wrap around the end of the series. In other
words, define moving blocks (assuming $l > 1$) as:
\jy{Any equation must be a part of a sentence and should be punctuated.}
\jy{Recall a blank line means a new paragraph.}
\jy{Define your response command with color and respond}
\mc{addressed above comments}
\begin{equation}
Z_j =
    \begin{cases}
        \{X_j, \ldots, X_{j + l - 1}\} & \text{if } j = 1, \dots, n - l + 1\\
        \{X_j, \ldots, X_n, X_1, \ldots, X_{j-n+l-1}\} & \text{if } j = n - l
        + 2 ,\dots, n.
    \end{cases}
\end{equation}
\jy{The ending index does not seem right}
\mc{addressed above}
The second version of moving block bootstrap was used in
this study because it is the implementation provided in the function
\texttt{tsboot} from R package \textsl{boot} \citep{boot}, and it is easier
overall because $l$ need not divide $n$.
\jy{state we use it because it is implemented in package boot and cite boot}  
\jy{This reference is from a low-tier journal. Find something from a stronger
  journal?}
\mc{addressed above comments}
The block size~$l$ needs to chosen with care. It needs to be large enough for
each bootstrap sample to preserve the serial dependence, yet small enough for
there to be some variability between each bootstrap sample. As $n$ increases,
$l$ should also increase, but $l / n$ should decrease. To achieve this, $l$ is
often assigned a value as a function of $n$. A common function that is
considered the best by much previous literature is $l = \lceil n^{1/3} \rceil$
\citep{buhlmann1999block}.

@@

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
In this study, the $BC_a$ CI is an interval centered at the point estimator.
\eds{a different abbrevation/notation was used for this in the introduction}
\mc{used $BC_a$}
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{G}(c) = \#\{\hat\theta_n^{(b)} < c\}/B$ for $b \in \{1, \ldots, B\}$, let
$z_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$ for $b \in \{1, \ldots, B\}$, let
$\hat{\theta}_{n, -i}$ be the statistic of the sample without the $i^{th}$
block, and let $a$ be $SKEW\{\hat{\theta}_{n, -i}\} / 6$. Then
 $\hat\theta_{BC_a}[\alpha] = \hat{G}^{-1}\Phi(z_0 + \frac{z_{0} + z_{\alpha}}{1 - a(z_{0} + z_{\alpha})}).$ \eds{notation will need to be cleaned and clarified}
A $(1 - \alpha)$ centered $BC_a$ CI is
\[
(\hat\theta_{BC_a}[\alpha/2], \quad
\hat\theta_{BC_a}[1 - \alpha/2]).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. 
\jy{why is it called BCA?}
\mc{addressed}

@@

\jy{Make it flow better and conciser}
The coverage rates of the CIs were used to compare the performance of CIs. Let
$\hat\theta_{L, r}$ and $\hat\theta_{U, r}$ be the lower and upper bound,
respectively, for the confidence interval constructed for each replicate
$r \in \{1, \ldots, R\}$, where $R$ is the
number of replicates.
Then $cov = \#\{\hat\theta_{L, r} < \theta < \hat\theta_{U, r} \}/R$,  
for $r \in \{1, \ldots, R\}$.
\eds{this notation is a bit sloppy, as it implies $n_{CI}$ changes for each 
value of $CI$; consider using a summation of indicators with a different index}
\mc{replaced $CI$ with $r$, and $n_{CI}$ with $R$}
The coverage rate is, of course, a
point estimate of a proportion, so a 95\% CI of this coverage
proportion (with $n_{CI} = 10000$) can be constructed. If the proportion
0.95 is included in the interval, the block bootstrap method is likely
performing
well. If all values in the interval are below 0.95, the results would suggest 
that the
method either is providing inaccurate estimation, is underestimating the
process' variability, or a combination of both. If all values in the interval
are above .95, the results suggest that the method is overestimating the
process' variability.

@@

Block bootstrap is a useful method for estimating parameters of a time
series, from simple parameters like the mean to more complicated temporal
 dependence factors.
%The motivation for the study is the idea that block bootstrap procedure will
%perfectly estimate a parameter of a time series given an infinitely large
%sample. The goal for this study was to find what is a good enough finite
%sample length for block bootstrap estimation to recover the parameter of a
%time series at an acceptable rate.
 We know theoretically that the block bootstrap procedure will cover
 \eds{? interval will correctly cover?  What does the theory  actually say?}
 \mc{addressed} a
 parameter of a time series at the nominal level given an
 infinitely large
sample, so the goal for this study was to find the smallest finite
sample length $n$ of a time series in order for the block bootstrap procedure
to 
recover its associated parameters at an acceptable rate.

Again, this analysis \eds{what?} \mc{addressed} relies on the assumption that
there is a size $n$ large enough for the method to work: that is, the method's
performance improves as $n$ increases. Out of the two types of intervals used
in this study, this assumption was found to hold true with respect to
estimating $\phi$ only for $\hat{\theta}_{n}$-centered intervals, whereas both
percentile and $BC_a$ intervals exhibited coverage deterioration as $n$
increased.
